---
title: "HLS_bulkdownload"
format: html
filters:
  - grouped-tabsets
environments: [program]
editor: visual
---

# How to: Bulk Query HLS data with NASA's CMR-STAC API

## Objectives

-   Access [**H**armonized **L**andsat **S**entinel](https://lpdaac.usgs.gov/data/get-started-data/collection-overview/missions/harmonized-landsat-sentinel-2-hls-overview/) product data through [NASA's CMR-STAC API](https://cmr.earthdata.nasa.gov/search/site/docs/search/api.html)

-   Perform large queries (requests that return more than 2000 granules)

-   Prepare a list of URLs representing query

## Define Environment:

::: panel-tabset
## R

```{r}
library(httr)
library(purrr)
library(jsonlite)
library(DT)
library(magrittr)
library(xml2)
library(dplyr)
library(reticulate)
library(usethis)
library(gitcreds)

usethis::create_github_token()
usethis::git_sitrep()

#setup for Python Installation:
# install SciPy
conda_install("r-reticulate", "aiohttp")
conda_install("r-reticulate", "requests")

# import SciPy (it will be automatically discovered in "r-reticulate")
aiohttp <- import("aiohttp")
requests <- import("requests")




```

## Python

```{python}
import requests
import math
import aiohttp 
import asyncio
import time
```
:::

## Define parameters needed for search:

1.  **URL**, for the LPCLOUD catalog

::: panel-tabset
## R

```{r}
lpcloud_url <- "https://cmr.earthdata.nasa.gov/stac/LPCLOUD/search"
```

## Python

```{python}
lpcloud_url = 'https://cmr.earthdata.nasa.gov/stac/LPCLOUD/search'
```
:::

2.  **Collection ID**, as a list

::: panel-tabset
## R

```{r}
c <- list("HLSS30.v2.0", "HLSL30.v2.0")
```

## Python

```{python}
c = ['C2021957657-LPCLOUD', 'C2021957295-LPCLOUD']
```
:::

3.  **Date-Time**, specified as `YYYY-MM-DDTHH:MM:SSZ/YYYY-MM-DDTHH:MM:SSZ` where: YYYY = year (ie., 2002), MM = month (ie., January = 01), DD = day of month, HH = hour, MM (second appearance) = minute, SS = second, Z = constant (part of the temporal query definition)

::: panel-tabset
## R

```{r}
d <- '2000-01-01T00:00:00Z/2001-01-31T23:59:59Z'
```

## Python

```{python}
d = '2000-01-01T00:00:00Z/2001-01-31T23:59:59Z'
```
:::

4.  **Lower Left and Upper Right Coordinates of Spatial Bounding Box**, in decimal degrees - can draw a spatial bounding box [here](http://geojson.io/#map=2/20.0/0.0)

::: panel-tabset
## R

```{r}
b <- '-122.0622682571411,39.897234301806,-122.04918980598451,39.91309383703065'
```

## Python

```{python}
b = '-122.0622682571411,39.897234301806,-122.04918980598451,39.91309383703065'
```
:::

## Search:

words

::: panel-tabset
## R

```{r}
SearchResults <- httr::POST(lpcloud_url, 
                       body = list(collections = c,
                                   datetime = d,
                                   bbox = b,
                                   page_size = 2000), encode = "json") %>% 
  httr::content(as = "text") %>%  
  jsonlite::fromJSON()


names(response)
```

## Python

```{python}
SearchResults = requests.get(lpcloud_url, 
                        params={
                            'concept_id': c, # collections
                            'temporal': d,   # datetime_range
                            'page_size': 2000,
                            },
                        headers={
                            'Accept': 'application/json'
                            }
                       )
print(SearchResults.status_code)
```
:::

## View Results:

Run this function to view your results in a searchable data table.

    ViewSearchResults <- function(SearchResults) {
          granule_list <- list()
          n <- 1
          for(row in row.names(response$features)){
            f <- response$features[row,]
            for (b in f$assets){
              df <- data.frame(Collection = f$collection,
                               Granule_ID = f$id,
                                 Datetime = f$properties$datetime,
                               Asset_Link = b$href, stringsAsFactors=FALSE)
              granule_list[[n]] <- df
              n <- n + 1
            }
          }
          
          search_df <- do.call(rbind, granule_list)
          DT::datatable(search_df)
    }

### Contact Information

**Material written by Bri Lind^1^, Erik Bolch^1^, Mahsa Jami^1^, and Aaron Friesz^1^**\
Contact: [LPDAAC\@usgs.gov](mailto:LPDAAC@usgs.gov){.email}\
Voice: +1-866-573-3222\
Organization: Land Processes Distributed Active Archive Center (LP DAAC)\
Website: <https://lpdaac.usgs.gov/> \
Date last modified: Summer-2022

^1^ KBR, Inc., contractor to the U.S. Geological Survey, Earth Resources Observation and Science (EROS) Center, Sioux Falls, South Dakota, USA. Work performed under USGS contract G0121D0001 for LP DAAC^2^.

^2^ LP DAAC Work performed under NASA contract NNG14HH33I.
